Contact mechanics, or the modeling of the impossibility of interpenetration of solid objects, is fundamental to computational solid mechanics (CSM) applications yet are oftentimes the most challenging in terms of computational efficiency and performance.

These challenges arise from the irregularity and highly dynamic nature of contact problems, particularly with algorithms designed for distributed memory architectures. First among these challenges is the inherent load imbalance when distributing contact load across compute nodes. This imbalance is highly problem dependent, and relates to the surface area of contact manifolds and the volume around them, rather than the distribution of the mesh over compute nodes, meaning the application load can vary drastically over different phases. The dynamic nature of contact problems motivates the use of distributed asynchronous many-tasking (AMT) frameworks to efficiently handle irregular workloads.

In this paper, we present our work on \_distBVH\_, a distributed contact solution using the DARMA/vt library for asynchronous tasking that is also capable of running on-node Kokkos-based kernels. We explore how \_distBVH\_ addresses the various challenges of CSM contact problems. We evaluate the use of many of DARMA/vt's dynamic load balancers, including decentralized load balancers such as \_TemperedLB\_, and demonstrate how our load balancing approach can provide significant performance improvements on various computational solid mechanics benchmarks. Additionally, we show how our approach can take advantage of DARMA/vt for tasking and efficient on-node kernels using Kokkos to scale over hundreds of processing elements.
